prolfqua - An R-package for Proteomics Differential Expression Analysis.

### 2022-05-05 inst/MyArticle/paper.Rmd
code snippet for MSFragger

The following code snipet demomnstarte the usage from MSFragger ouput.

```{r}

>>>>

The following code demonstrates how an analysis of MSFragger ouput can be performed using prolfqua.

```{r}
datadir <- file.path(find.package("prolfquadata") , "quantdata")
inputFragfile <-  file.path(datadir, "MSFragger_IonStar2018_PXD003881.zip")
inputAnnotation <- file.path(datadir, "annotation_Ionstar2018_PXD003881.xlsx")
# read input annotation
annotation <- readxl::read_xlsx(inputAnnotation)

protein <- tibble::as_tibble(read.csv(unz(inputFragfile,"IonstarWithMSFragger/combined_protein.tsv"),
                             header = TRUE, sep = "\t", stringsAsFactors = FALSE))

# read combined_protein.tsv 
protein <- prolfqua::tidy_MSFragger_combined_protein(protein)
# remove proteins identified by a single peptide
protein <- protein |> dplyr::filter(unique.stripped.peptides > 1)

# annotate the data
merged <- dplyr::inner_join(annotation, protein)

atable <- prolfqua::AnalysisTableAnnotation$new()
atable$fileName = "raw.file"
# specify column containing protein identifiers
atable$hierarchy[["protein_Id"]] <- c("protein")

# column with protein abundances
atable$setWorkIntensity("total.intensity")

# the factors of the analysis
atable$factors[["dilution."]] = "sample"
atable$factors[["run"]] = "run_ID"

config <- prolfqua::AnalysisConfiguration$new(atable)

adata <- prolfqua::setup_analysis(merged, config)
lfqdata <- prolfqua::LFQData$new(adata, config)
# remove small intensities
lfqdata$remove_small_intensities()
